Dragonfly Territory Ananlysis

### 2020-11-29 analysis/analysisSS.Rmd
working on plots, had to rename data file

rawDragonfly <- `DataSingleStudy`

@@

plot(abunYearsSums$year, abunYearsSums$total_abundance)

# I want plots for all 10 species

@@

fitBPratense <- lm(bPratenseCompAY$bPratenseAbundance ~ bPratenseCompAY$YEAR)

>>>>

DataSingleStudy <- read.csv("~/GitHub/rrirfinalproject/DataSingleStudy")
rawDragonfly <- `DataSingleStudy`

@@

par(mfrow=c(1,1))
plot(abunYearsSums$year, abunYearsSums$total_abundance, xlab = "Year", ylab = "Abundance")
abline(lm(abunYearsSums$total_abundance ~ abunYearsSums$year), col="red")

fitTotal <- lm(abunYearsSums$total_abundance ~ abunYearsSums$year)

summary(fitTotal)

pValueTotal <- 0.000162

# I want plots for all 10 species with a trend line

@@

# I want to see if these are significant, so I am going to save the lm and then I will do a summary of each one

fitBPratense <- lm(bPratenseCompAY$bPratenseAbundance ~ bPratenseCompAY$YEAR)
summary(fitBPratense)
pValueBPratense <- 0.5911

fitPNymphula <- lm(pNymphulaCompAY$pNymphulaAbundance ~ pNymphulaCompAY$YEAR)
summary(fitPNymphula)
pValuePNymphula <- 0.02333

fitACyanea <- lm(aCyaneaCompAY$aCyaneaAbundance ~ aCyaneaCompAY$YEAR)
summary(fitACyanea)
pValueACyanea <- 0.3033

fitSSanguineum <- lm(sSanguineumCompAY$sSanguineumAbundance ~ sSanguineumCompAY$YEAR)
summary(fitSSanguineum)
pValueSSanguineum <- 0.00009631

fitAGrandis <- lm(aGrandisCompAY$aGrandisAbundance ~ aGrandisCompAY$YEAR)
summary(fitAGrandis)
pValueAGrandis <- 0.1363

fitCPuella <- lm(cPuellaCompAY$cPuellaAbundance ~ cPuellaCompAY$YEAR)
summary(fitCPuella)
pValueCPuella <- 8.362e-07

fitIElegans <- lm(iElegansCompAY$iElegansAbundance ~ iElegansCompAY$YEAR)
summary(fitIElegans)
pValueIElegans <- 0.103

fitLSponsa <- lm(lSponsaCompAY$lSponsaAbundance ~ lSponsaCompAY$YEAR)
summary(fitLSponsa)
pValueLSponsa <- 0.0001868

fitLQuadrimaculata <- lm(lQuadrimaculataCompAY$lQuadrimaculataAbundance ~ lQuadrimaculataCompAY$YEAR)
summary(fitLQuadrimaculata)
pValueLQuadrimaculata <- 0.0359

fitSStriolatum <- lm(sStriolatumCompAY$sStriolatumAbundance ~ sStriolatumCompAY$YEAR)
summary(fitSStriolatum)
pValueSStriolatum <- 0.9176
